Supplementary Information

### 2015-06-19 manuscript/latitudepaper.tex
trying out the new figs
Updated figures in many ways

  Unlike species richness, only generality showed an overall increase with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estaurine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
  The strength of this scaling decreased towards the poles in estuarine,
  lake, marine, and stream communities in each case
  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
  Fig~\ref{I}). In terrestrial communities, however, scaling was stronger
  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
  vulnerability, respectively).

  In contrast, link density, generality, and vulnerability decreased as the
  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
  food webs the strength of this scaling did not
  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
  best-fit model for generality did not include any terms for latitude in
  any ecosystem type). In stream and terrestrial food webs, scaling was more
  strongly negative in the tropics and did not differ from zero near the poles,
  although this trend was only significant in streams
  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{T}).

@@

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{B}
\end{figure}

\newpage

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}

>>>>

  Unlike species richness, only generality showed an overall increase with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estaurine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{BIT}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
  The strength of this scaling decreased towards the poles in estuarine,
  lake, marine, and stream communities in each case
  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
  Fig~\ref{BIT}). In terrestrial communities, however, scaling was stronger
  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
  vulnerability, respectively).

  In contrast, link density, generality, and vulnerability decreased as the
  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
  food webs the strength of this scaling did not
  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
  best-fit model for generality did not include any terms for latitude in
  any ecosystem type). In stream and terrestrial food webs, scaling was more
  strongly negative in the tropics and did not differ from zero near the poles,
  although this trend was only significant in streams
  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{BIT}).

@@

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empiricl food webs. 
Exponents for the scaling of generality and vulnerability with species richness were very 
similar to those for link density, except for the scaling of generality in streams where 
the size of the exponent increased towards the poles. See \emph{Fig. S2, Appendix 5} for 
all scaling relationships.}
\label{S}
\end{figure}

\begin{figure}[!H]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.
Exponents for the scaling relationships of generality and vulnerability with each proportion were very
similar to those of the scaling relationships with link density, except for the scaling of generality
with the proportion of top predators where there was no effect of latitude on the size of the exponent
in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}

### 2015-06-19 manuscript/supplement.tex
Updated figures in many ways

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{}
\caption{ }
\label{}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{B}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}
